Noisy Learning

### 2023-11-20 Model/deOptim_alm.qmd
rearrange files; package loading

purrr::walk(here::here(c("Functions/Display_Functions.R","Functions/misc_model_funs.R",
                         "Functions/alm_core.R","Functions/fit_funs.R")),source)
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))

ds <- ds |> mutate(sbj=id)
dsAvg <- ds |> group_by(condit,expMode2,tr, x) |> 
  summarise(y=mean(y),.groups="drop")

@@

library(DEoptim)

de_optim_fit <- function(func, fit_params, model_params, dat_params, initial_params) {

 purrr::walk(here::here(c("Functions/misc_model_funs.R","Functions/alm_core.R","Functions/fit_funs.R")),source)
  model_fun = get(func)
  train_data <- dat_params$train_data
  test_data <- dat_params$test_data
  test_avg <- dat_params$test_avg
  pred_dat <- get(fit_params$pred_dat)
  loss_dat <- fit_params$loss_data
  pred_fun <- match.fun(fit_params$pred_fun)
  loss_fun <- match.fun(fit_params$loss_fun)
  initial_params <- initial_params
  list2env(model_params,envir = environment())
  # Define the objective function for DEoptim
  objective_function <- function(params) {
    model_fun(params, pred_dat, pred_fun, loss_fun, loss_dat, model_params, test_data, train_data)
  }

  # Define bounds for parameters
  lower_bounds <- c(.01,.1,10)
  upper_bounds <- c(5,5,2000)
  initialpop=initial_params

  # Define number of particles (NP) and iterations (maxiter)
  NP <- 10 * length(initial_params) + 1
  maxiter <- 200
  strategy=6

  optim_time <- system.time({
    # Using DEoptim instead of JDEoptim
    de_optim_res <- DEoptim(fn = objective_function, lower = lower_bounds, 
                            upper = upper_bounds, control = list(NP = NP, itermax = maxiter,strategy=strategy))
  })

  bestFit <- as.data.frame(as.list(de_optim_res$optim$bestmem)) |> mutate(Value=round(de_optim_res$optim$bestval,3))
  names(bestFit) <- c("c","lr","sigma","value")

  bf_train_result <- alm.sim(train_data, bestFit$c, bestFit$lr, input.layer, output.layer)
  weight.mat <- bf_train_result$wm
  bf_train <- bf_train_result$d
  best_preds <- map_dbl(pred_dat$x, ~ pred_fun(.x, bestFit$c,input.layer, output.layer, weight.mat,trainVec))
  (bf_test <- cbind(pred_dat, pred = best_preds ))

  if (any(is.nan(best_preds))) {
  warning("Warning: test_prediction contains NaN values.")
}

  if(length(is.null(bestFit$sigma))){
  train_error <- loss_fun(bf_train$y, bf_train$almResp,bestFit$sigma) |> as.numeric()
  test_error <- loss_fun(pred_dat$y, best_preds,bestFit$sigma |> as.numeric())
  } else{
    train_error <- loss_fun(bf_train$y, bf_train$almResp)
    test_error <- loss_fun(pred_dat$y, best_preds)
  }

  print_b <-paste0(strip_list_notation(tibble::lst(round_tibble(bestFit,3))))
  print(paste0(print_b, ",  time:",  round(optim_time[3],1)))

  optim_info <- list(id=as.numeric(train_data$sbj[1]),condit=as.character(train_data$condit[1]),
                     Value = bestFit$Value, c = bestFit$c, lr = bestFit$lr, 
                     print_b,
                     NAN_Test=any(is.nan(best_preds)),
                     model_fun=func, 
                     pred_fun=fit_params$pred_fun,
                     loss_dat=loss_dat,loss_fun=fit_params$loss_fun, 
                     train=bf_train,test=bf_test, Fit = bestFit, 
                     train_error=train_error,test_error=test_error,
                     run_args=tibble::lst(func,fit_params,model_params,dat_params,trainVec,input.layer,output.layer),
                     opt_info=tibble::lst(de_optim_res,initial_params, NP, maxiter, lower_bounds,upper_bounds),
                     info=tibble::lst(time=Sys.time(),Sys.info(), path=getwd()),
                     runtime=optim_time[3])

  return(optim_info) 
}

de_optim_fit_id <- function(id_data, func, fit_params, model_params, initial_params) {
  train_data <- id_data %>% filter(expMode2=="Train") # Adjust condition as needed
  test_data <- id_data %>% filter(expMode2=="Test") # Adjust condition as needed
  test_avg <- test_data |> ungroup() |>  group_by(sbj,x,condit) |> summarise(y=mean(y), .groups="drop")

  dat_params <- tibble::lst(test_data = test_data, train_data = train_data, test_avg=test_avg)

  # Wrap the optimization call in tryCatch
  result <- tryCatch({
    de_optim_fit(func, fit_params, model_params, dat_params, initial_params)
  }, error = function(e) {
    message("Error during optimization for ID ", unique(id_data$id), ": ", e$message)
    return(NULL) # Return NULL or another error indicator
  })

}

@@

>>>>

purrr::walk(here::here(c("Functions/Display_Functions.R","Functions/misc_model_funs.R",
                         "Functions/alm_core.R","Functions/fit_funs.R")),source)
ds <- readRDS(here::here("data/e1_md_11-06-23.rds")) |> mutate(sbj=id)

dsAvg <- ds |> group_by(condit,expMode2,tr, x) |> 
  summarise(y=mean(y),.groups="drop")

@@

@@

```{r}
# 11/16/23 - fairly successful fits
